### 2014-03-22 doc/report/article.tex
Pierwszy commit

\documentclass[a4paper]{article}
\usepackage{polski}
\input{packages-article}
%\title{}
%\author{Mateusz Grotek}
%\date{}
%\thanks{}
\begin{document}
\(2{,}3\)
\TeX
%\maketitle
%\begin{abstract}\centering
%\end{abstract}
%\tableofcontents
\end{document}